%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - Cover Letter Template
% LaTeX Template
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-cover-letter-openfont}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{fontspec}
\usepackage{graphicx}

 
\pagestyle{empty}
\fancyhf{}
 
\rfoot{Page \thepage \hspace{0pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Thomas}{Williams}{ % Your name
    47 Headgate Rd, Damariscotta, Maine 04543\\
    207.350.0989 - \href{mailto:thomaslodgewilliams@gmail.com}{thomaslodgewilliams@gmail.com}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     MAIN COVER LETTER CONTENT
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\hfill

\begin{minipage}[t]{0.5\textwidth} 
\companyname{The Franklin Institute}
\companyaddress{
ATTN: Human Resources Department \\
222 North 20th Street \\
Philadelphia, PA 19103
}
\end{minipage}
\begin{minipage}[t]{0.49\textwidth} 
\currentdate{\today}
\end{minipage}

\lettercontent{Dear Franklin Institute Human Resources Staff,}

\lettercontent{I have been to dozens of museums around the world, and perhaps the only one I have been to more than once, and actually with some consistency, is the Franklin Institute. Almost every year, my family has made excursions to see special or regular exhibits, an IMAX show or travel to other worlds in the Observatory. From an early age, I loved the Franklin Institute because of its interactive learning and almost play-like environment. This aligns with and has informed my own learning style and subsequent work desires.}

\lettercontent{The position of Escape Room Game Master appeals to me greatly because it combines that interactive learning with participatory game-like storytelling. Much like the games of
Dungeons and Dragons I run for friends, an Escape Room allows for story-driven puzzles and challenges that build group dynamics. By providing effective but clever clues, an Escape Room forces critical thinking in an environment that feels like a game. Getting to help create an Escape Room experience at the Franklin Institute would be an exciting, interactive learning experience for both patrons and myself.}

\lettercontent{Visits to places like the Franklin Institute have helped develop my strong sense of curiosity and love for learning. I am truly enthusiastic when interacting with new people
and concepts. My college experience melding art, architecture, and engineering with activities like chorale, orchestra, and radio station on-air support, strengthened and diversified my curiosity and passion for learning. Hosting a weekly role-playing game has taught me that playing can be learning, and learning can be playing.}

\lettercontent{It would be a thrill to bring my ingenuity, diverse interests, music and theater skills to Franklin Institute’s Escape Room. The museum’s mission to inspire a spirit of inquiry
and discovery has kept me coming back. I would be delighted to have the opportunity to do the same for the museum’s Escape Room visitors.}

\lettercontent{I look forward to the opportunity to meet with you to discuss how my qualifications align with the position of Escape Room Game Master at the Franklin Institute.}

\closing{Sincerely,}

\signature{Thomas Lodge Williams \\
Email: thomaslodgewilliams@gmail.com \\
Phone: 207.350.0989 \\
Website: thomaslodgewilliams.com}

\end{document}  